---
title: Carob report
output: html_document
editor_options: 
  chunk_output_type: console
md_extensions: -autolink_bare_uris
params:
  group: ""
  uri: ""
  records_file: ""
  metadata_file: ""
  messages_file: ""
  evaluation_file: ""
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)

scrolltab <- function(data, caption, width="100%") {
  rownames(data) <- NULL
  kableExtra::kbl(data, caption=caption) |>
    kableExtra::kable_classic(full_width = F,  position = "right") |>
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))  |> 
    kableExtra::scroll_box(width=width, height="400px")
}

ktab <- function(data, caption) {
    kableExtra::kbl(data, caption=caption) |>
    kableExtra::kable_classic(full_width=FALSE) |> 
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
}

group <- params$group
uri <- params$uri
f <- params$records_file
fmsg <- params$messages_file
fqc <- params$evaluation_file

if (!nzchar(f) || !file.exists(f)) {
  knitr::knit_exit("records file not found")
}

suri <- if (nzchar(uri)) yuri::simpleURI(uri) else "report"
huri <- if (nzchar(uri)) yuri:::http_address(uri) else ""
http <- if (nzchar(huri)) paste0('<a href="', huri, '">original data</a>') else "original data"
github <- paste0("https://github.com/reagro/carob/blob/master/scripts/", group, "/", suri, ".R")
script <- if (nzchar(group) && nzchar(suri)) paste0('<a href="', github, '">R script</a>') else "R script"
```

```{r setup2, include=FALSE}
d <- utils::read.csv(f, stringsAsFactors = FALSE)
m <- utils::read.csv(params$metadata_file, stringsAsFactors = FALSE, nrows = 1)
license <- trimws(gsub("license", "", m$license))
if (nzchar(fmsg) && file.exists(fmsg)) {
  have_msg <- TRUE
  msg <- utils::read.csv(fmsg, stringsAsFactors = FALSE)
  warnings <- "The standardization script emits the following non-compliance warnings."
} else {
  have_msg <- FALSE
  warnings <- "The standardization script does not emit non-compliance warnings."
}

if (nzchar(fqc) && file.exists(fqc)) {
  have_qc <- TRUE
  qc <- utils::read.csv(fqc, stringsAsFactors = FALSE)
  qc <- round(t(qc[,-1]) * 100, 1)
  qc <- data.frame(variable=rownames(qc), `completeness`=qc[,1])
  rownames(qc) <- NULL
  names(qc) <- c("variable", "completeness (%)")
  qcmean <- round(mean(qc[,2]) / 10, 1)
  qctxt <- paste("The overall quality of the dataset, given the completeness of required variables was", qcmean, "on a scale of 10. See the table below")
} else {
  have_qc <- FALSE
  qctxt <- ""
}

tvars <- m$treatment_vars
treatments <- NULL 

if (!is.null(tvars) && !is.na(tvars)) {
   tvars <- trimws(unlist(strsplit(tvars, ";")))
   tvars <- tvars[!(tvars %in% c("none", "longitude", "latitude"))]
   tvars <- tvars[(tvars %in% names(d))]
   ntreats <- length(tvars)
   if (ntreats > 0) {
     treatments <- unique(tvars)
     treatments <- paste(sort(treatments), collapse=", ")
   }
}

get_values <- function(x, label) {
  x <- unique(x)
  ifelse(length(x)==1, x, paste0(length(x), " ", label, " (", paste(sort(x), collapse=", "), ")"))
}

crop <- if ("crop" %in% names(d)) get_values(d$crop, "crops") else ""
country <- if ("country" %in% names(d)) get_values(d$country, "countries") else ""

locvars <- c("country", paste0("adm", 1:5), "location", "site", "longitude", "latitude")
locvars <- locvars[locvars %in% colnames(d)]
locs <- unique(d[, locvars, drop=FALSE])
if (all(c("longitude", "latitude") %in% colnames(locs))) {
	xy <- unique(locs[, c("longitude", "latitude")])
	xytxt <- paste0("We have coordinates for ", nrow(xy), " of these locations.")
	noxy <- is.na(d$latitude) | is.na(d$longitude)
	if (any(noxy)) {
		xytxt <- paste(xytxt, sum(noxy), "records do not have coordinates.")
	}
	xy <- xy[!noxy, ,drop=FALSE]	
	haveXY <- nrow(xy) > 0
} else {
	xytxt <- paste0("We do not have coordinates for these locations.")
	xy <- cbind(0,0)[0,]
	haveXY <- FALSE
}


if (grepl("trials", group)) {
	varieties <- unique(d$variety)
	if (is.null(varieties))	varieties <- unique(d$variety_code)
   vartxt <- paste(" These are trial data for", length(varieties), "varieties.") 
} else {
	vartxt <- ""
}
   
   
hta <- if (!is.na(m$publication)) gsub("_", "/", yuri:::http_address(m$publication)) else ""
pub <- ifelse(is.na(m$publication), "", paste0('You can also consult the accompanying <a href="', hta, '">paper</a>.'))


zipf <- paste0("https://geodata.ucdavis.edu/carob/zip/", suri, ".zip")
dwnl <- ""
if (grepl("CC", license)) {
	dwnl <- paste0(' Here you can <a href="', zipf, '">download</a>', " the standardized data.")
} else if (grepl("unknown", license)) {
	dwnl <- paste0(" Because of the license is not specified, you need to run the script yourself to get the standardized data.")
} else {
	dwnl <- paste0(" Because of the restrictions of this license, you need to run the script yourself to get the standardized data.")
} 

```


This report describes standardized data for "*`r m$title`*". These data were standardized on `r m$carob_date` by `r m$carob_contributor` with this `r script`. The `r http` have a `r license` [license](https://carob-data.org/licenses.html). `r dwnl`
</br>
</br>
This is the full citation of the data set: 

<div style="padding-left: 40px;">
<b>`r m$data_citation`</b>
</div>

`r pub`

The dataset has `r nrow(d)` records and `r ncol(d)` variables for `r crop` in `r country`. `r vartxt` `r if(!is.null(treatments)) paste0("The dataset has ", ntreats, " treatment(s): ", treatments, ".")`

</br>
These are the first `r min(nrow(d), 25)` records: 

```{r tab1}
d$dataset_id <- d$record_id <- NULL

scrolltab(head(d, 25), "records")
```


</br>

The observations were made at `r nrow(locs)` locations. `r xytxt`

```{r map, include=haveXY}
locs <- locs[!(is.na(locs$latitude) | is.na(locs$longitude)), ,drop=FALSE]
if (nrow(locs) > 0) {
  suppressMessages(library(terra))
  v <- terra::vect(locs, c("longitude", "latitude"), crs="+proj=longlat")
  terra::plet(v, cex=2, col="red")
}
```

</br>

`r warnings`

```{r msg, include=have_msg}
if (have_msg) {
  msg <- msg[,c("check", "msg")]
  names(msg) <- c("type", "message")
  ktab(msg, "")
}
```

`r qctxt`

```{r qc, include=have_qc}
if (have_qc) {
  ktab(qc, "")
}
```

</br>
The data are further summarized in the table below.

```{r summary, fig.width=6}
d$longitude <- d$latitude <- NULL
dfs <- summarytools::dfSummary(d, varnumbers=FALSE, graph.magnif=0.75, 
                               max.string.width=20, display.labels=FALSE, valid.col=FALSE, 
							  )
summarytools::view(dfs, method = "render", 
                    report.title="", max.tbl.height = Inf)
```
